---
title: "Final Project- Co2 Emissions"
author: "Sai Mulagan"
date: "12/6/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Summary of data set
```{r}
library(readr)
library(stringr)
CARbon=read.csv("CO2 Emissions_Canada.csv",header = TRUE)
str(CARbon)
mean(CARbon$CO2.Emissions.g.km.)
```
plotting Engine size and Carbon Emissions
```{r}
library(tidyverse)
CARbon%>%
ggplot(aes(x=Engine.Size.L.,y=CO2.Emissions.g.km.))+
  geom_point(alpha=0.5)+ 
  ggtitle("Engine size vs Emissions") +
  xlab("Engine Size (Liters)") + ylab("Carbon Emissions")
```
Correlation is strong positive relationship
```{r}
cor(CARbon$Engine.Size.L.,CARbon$CO2.Emissions.g.km.)
```


plotting Cylinders and Carbon Emissions
```{r}
boxplot(CO2.Emissions.g.km.~Cylinders,data=CARbon, main="Cylinders vs Emissions",
   xlab="Number of Cylinders", ylab="Carbon Emissions")
```
Correlation is strong positive relationship
```{r}
cor(CARbon$Cylinders,CARbon$CO2.Emissions.g.km.)
```
plotting Fuel Consumption and Carbon Emissions
```{r}
CARbon%>%
  ggplot(aes(x=Fuel.Consumption.Comb..mpg.,y=CO2.Emissions.g.km.))+
  geom_point(alpha=0.5)+
  ggtitle("Fuel Consumption vs Emissions") +
  xlab("Fuel Consumption (mpg)") + ylab("Carbon Emissions")
```
Correlation is strong positive relationship
```{r}
cor(CARbon$Fuel.Consumption.Comb..mpg.,CARbon$CO2.Emissions.g.km.)
```
R squared value is 0.9274. This shows how all Variables are important to find carbon emissions. Most important is fuel type.
```{r}
linear_model<-lm(CO2.Emissions.g.km.~Engine.Size.L.+Cylinders+Fuel.Consumption.Comb..mpg.+Fuel.Type,CARbon)
linear_model
summary(linear_model)

```
Equation to find carbon emissions of a car: CO2.Emissions.g.km.=377.171 + (7.30119*Engine.Size.L.) +(6.34945*Cylinders)+(-5.76000*Fuel.Consumption.Comb..mpg.)+(-74.24595*Fuel.TypeE) +(-101.83172*Fuel.TypeN)+(-23.38014*Fuel.TypeX)+(-27.14213*Fuel.TypeZ)
```{r}
Engine.Size.L.=0.5
Cylinders=2
Fuel.Consumption.Comb..mpg.=80
Fuel.Type='X'

single_obs<-data.frame(Engine.Size.L.=0.5,Cylinders=2,Fuel.Consumption.Comb..mpg.=60,Fuel.Type='X')
predict(linear_model,single_obs)

```

